Thermodynamic fragments in magic state theories

### 2020-07-15 magic_paper.tex
Comment on bounds

Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
\begin{equation}
	\Phi(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}.
\end{equation}
Let $\Phi_+(m; n, p)$ denote the same sum but only considering the even indices, $j = 0, 2, \dots, m$ and similarly let $\Phi_-(m; n, p)$ denote the same sum but only considering the odd indices, $j = 1, 3, \dots, m$.

Assume $n$ is even, so that $\bar n = n$.
Then we can express any elbow on the $n$-copy Strange state Lorenz curve as
\begin{align}
	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right) \label{eq:leftelb}\\
	L_-(m; n) &= L_\star - \left(\frac{5}{3}\right)^n \Phi_-\left(m;n,\frac{1}{5}\right), \label{eq:rightelb}
\end{align}
where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ indicate points on the left, right of the curve respectively for some index $m$.

The locations of the elbows are at
\begin{align}
	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right) \\
	x_-(m; n) &= x_\star + \Phi_-\left(m;n,\frac{1}{9}\right),
\end{align}
where $x_\star = x_+(n; n)$ is the location of the maximum.

>>>>

Denote by $\Phi(m; n, p)$ the cumulative binomial distribution,
\begin{equation}
	\Phi(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}.
\end{equation}
Let $\Phi_+(m; n, p)$ denote the same sum but only considering the even indices, $j = 0, 2, \dots, m$ and similarly let $\Phi_-(m; n, p)$ denote the same sum but only considering the odd indices, $j = 1, 3, \dots, m$.
Then,
\begin{align}	
	\Phi_+ + \Phi_- &= \Phi \\
	\Phi_+ - \Phi_- &= \Phi^c \coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j}.
\end{align}

\nick{$\Phi$ is bounded by the two exponentials in Wikipedia ONLY for $m\leq np$ so these bounds do not hold for $m>np$.

$\Phi^c$ is NOT bounded above by setting $m=n$ (which yields $(1 - 2p)^n$) and NOT bounded below by 0 - both due to the existence of negative terms in the sum.
It does appear however to be strictly within the open interval $(-1, 1)$.}

Assume $n$ is even, so that $\bar n = n$.
Then we can express any elbow on the $n$-copy Strange state Lorenz curve as
\begin{align}
	L_+(m; n) &= \left(\frac{5}{3}\right)^n \Phi_+\left(m;n,\frac{4}{5}\right), \label{eq:leftelb}\\
	L_-(m; n) &= L_\star - \left(\frac{5}{3}\right)^n \Phi_-\left(m;n,\frac{1}{5}\right), \label{eq:rightelb}
\end{align}
where $L_\star = L_+(n; n)$ is the maximum of the curve and $L_+, L_-$ indicate points on the left, right of the curve respectively for some index $m$.

The locations of the elbows are at
\begin{align}
	x_+(m; n) &= \Phi_+\left(m;n,\frac{8}{9}\right), \\
	x_-(m; n) &= x_\star + \Phi_-\left(m;n,\frac{1}{9}\right),
\end{align}
where $x_\star = x_+(n; n)$ is the location of the maximum.
